Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-20 paper/paper.tex
Add latest version of the paper

The study of Bettenburg et. al \cite{bettenburg2008makes} showed what 
makes for a valuable bug report through qualitative analysis. 
After conducting interviews with over 450 developers, one of the main factors
behind a quality ticket is grammar correctness in summary and description. Another
aspect which was flagged as helpful by the interviewees was the presence of stack 
traces and steps to reproduce in tickets. A further contribution brought by the
authors to the community is the creation of a tool called Cuezilla which is able 
to automatically predict the quality of a bug report with an accuracy of around 40\%.

>>>>

The study of Bettenburg et. al \cite{bettenburg2008makes} showed what 
makes for a valuable bug report through qualitative analysis. 
After conducting interviews with over 450 developers, Bettenburg et. al concluded that one of the main factors
behind a quality ticket is grammar correctness in summary and description. Another
aspect which was flagged as helpful by the interviewees was the presence of stack 
traces and steps to reproduce in tickets. A further contribution brought by the
authors to the community is the creation of a tool called Cuezilla which is able 
to automatically predict the quality of a bug report with an accuracy of around 40\%.
